Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations

### 2021-03-26 papers/intro_paper/intro_paper.tex
mention the comparable bounds on dtau220 between 21r and 150914
minor update
minor typesetting change in appendix

More specifically, as expected, the single GW event providing the best constraint
on the least-damped QNM to date continues to be GW150914 $(\df{220}=0.05^{+0.11}_{-0.07}, 
\dtau{220}=0.07^{+0.26}_{-0.23})$. In addition, in the most agnostic and
conservative scenario where we combine the information from different
events using a hierarchical approach~\cite{Zimmerman:2019wzo,Isi:2019asy}, we obtain 
at $90\%$ credibility $(\df{220}=0.03^{+0.10}_{-0.09}, \dtau{220}=0.10^{+0.44}_{-0.39})$. Thus, 
our results constrain the frequency (decay time) of the least damped QNM to be within $\sim
10\%$ ($\sim 40\%$) of the GR prediction --- an improvement of a factor of $\sim 4$ ($\sim 2$) 
over the results obtained with the $\pSEOB$ model in Ref.~\cite{Abbott:2020jks}.

@@

\section{Correlation of the binary's total mass with the non-GR parameters}\label{sec:correlation}

As mentioned in the main text, for low-SNR events with negligible
higher-modes and for which only the post-merger is detectable, there
is a strong degeneracy between the binary's total mass and the non-GR
deviations $(\df{220}, \dtau{220})$. For those cases, only the
reconstructed frequency and damping time $(f_{220},\tau _{220})$ can
be independently measured from the data.

To justify this statement, in Fig.~\ref{fig:correlations} we show
corner plots that illustrate the correlations between the non-GR
parameters $(\df{220}, \dtau{220})$, the detector-frame total mass
$M(1+z)$ and the reconstructed frequency and damping time
$(f_{220},\tau _{220})$ for GW150914 (left panel), corresponding to an
event for which both the pre- and post-merger phase are measurable,
and for GW190521 (right panel), an event in which the post-merger has
${\rm SNR}> 8$, but the pre-merger has an SNR below 8. For GW190521,
due the strong degeneracy between $\df{220}$ and $M(1+z)$, the 1D
posterior for $M(1+z)$ is pushed towards the upper boundary of its
prior, despite the very wide prior employed in the analysis. This in
turn renders the measurement of $\df{220}$ (and to a lesser degree of
$\dtau{220}$) highly dependent on the upper boundary of the total mass
prior. On the other hand, this issue does not significantly affect the
posteriors for the reconstructed quantities $(f_{220},\tau _{220})$
which are well measured and nearly independent on the upper prior
boundary for $M(1+z)$.
%
This is to be contrasted with the results for GW150914. In this case, 
the extra information coming from the pre-merger phase allows to break 
the degeneracy between the non-GR parameters and the total mass, 
and therefore both $(\df{220}, \dtau{220})$ and $M(1+z)$ can 
be measured at the same time.

>>>>

More specifically, as expected, the single GW event providing the best constraint
on the least-damped QNM to date continues to be GW150914 $(\df{220}=0.05^{+0.11}_{-0.07}, 
\dtau{220}=0.07^{+0.26}_{-0.23})$, although the bounds on 
$\dtau{220}$ from GW150914 are comparable to GW190521\_074359, 
the second-most precisely measured event in our list.
In addition, in the most agnostic and
conservative scenario where we combine the information from different
events using a hierarchical approach~\cite{Zimmerman:2019wzo,Isi:2019asy}, we obtain 
at $90\%$ credibility $(\df{220}=0.03^{+0.10}_{-0.09}, \dtau{220}=0.10^{+0.44}_{-0.39})$. Thus, 
our results constrain the frequency (decay time) of the least damped QNM to be within $\sim
10\%$ ($\sim 40\%$) of the GR prediction --- an improvement of a factor of $\sim 4$ ($\sim 2$) 
over the results obtained with the $\pSEOB$ model in Ref.~\cite{Abbott:2020jks}.

@@

\section{Correlation of the binary's total mass with the non-GR parameters}
\label{sec:correlation}

As mentioned in the main text, for low-SNR events with negligible
higher-modes and for which only the post-merger is detectable, there
is a strong degeneracy between the binary's total mass and the non-GR
deviations $(\df{220}, \dtau{220})$. For those cases, only the
reconstructed frequency and damping time $(f_{220},\tau _{220})$ can
be independently measured from the data. To justify this statement, 
in Fig.~\ref{fig:correlations} we show
corner plots that illustrate the correlations between the non-GR
parameters $(\df{220}, \dtau{220})$, the detector-frame total mass
$M(1+z)$ and the reconstructed frequency and damping time
$(f_{220},\tau _{220})$ for GW150914 (left panel), corresponding to an
event for which both the pre- and post-merger phase are measurable,
and for GW190521 (right panel), an event in which the post-merger has
${\rm SNR}> 8$, but the pre-merger has an SNR below 8. For GW190521,
due the strong degeneracy between $\df{220}$ and $M(1+z)$, the 1D
posterior for $M(1+z)$ is pushed towards the upper boundary of its
prior, despite the very wide prior employed in the analysis. This in
turn renders the measurement of $\df{220}$ (and to a lesser degree of
$\dtau{220}$) highly dependent on the upper boundary of the total mass
prior. On the other hand, this issue does not significantly affect the
posteriors for the reconstructed quantities $(f_{220},\tau _{220})$
which are well measured and nearly independent on the upper prior
boundary for $M(1+z)$. This is to be contrasted with the results for GW150914. In this case, 
the extra information coming from the pre-merger phase allows to break 
the degeneracy between the non-GR parameters and the total mass, 
and therefore both $(\df{220}, \dtau{220})$ and $M(1+z)$ can 
be measured at the same time.
